---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```


# rjdmarkdown

[![Travis Build Status](https://img.shields.io/travis/AQLT/rjdmarkdown.svg?logo=travis)](https://travis-ci.org/AQLT/rjdmarkdown)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rjdmarkdown)](https://cran.r-project.org/package=rjdmarkdown)

## Overview

rjdmarkdown gives a set of functions to print nicely your models created by [RJDemetra](https://github.com/nbbrd/rjdemetra).

## Installation

rjdmarkdown relies on RJDemetra that requires Java SE 8 or later version.

```{r gh-installation, eval = FALSE}
# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("AQLT/rjdmarkdown")
```

## Usage

For the moment the only function developped is `print_regarima()` for regarima models  for $\LaTeX$ outputs (`format = "latex"`, the package booktabs and float must be used) and HTML outputs (`format = "html"`). 

The option `results='asis'` must be used in the chunk:

```{r, eval = FALSE}
library(RJDemetra)
library(rjdmarkdown)
myreg <- regarima_x13(ipi_c_eu[, "FR"])
print_regarima(myreg, format = "latex")
# or
print_regarima(myreg, format = "html")
```


