---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```


# rjdmarkdown

[![Travis Build Status](https://img.shields.io/travis/AQLT/rjdmarkdown.svg?logo=travis)](https://travis-ci.org/AQLT/rjdmarkdown)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rjdmarkdown)](https://cran.r-project.org/package=rjdmarkdown)
[![CRAN last release](http://www.r-pkg.org/badges/last-release/rjdmarkdown)](https://cran.r-project.org/package=rjdmarkdown)
[![CRAN monthly downloads](http://cranlogs.r-pkg.org/badges/rjdmarkdown?color=lightgrey)](https://cran.r-project.org/package=rjdmarkdown)
[![CRAN downloads](http://cranlogs.r-pkg.org/badges/grand-total/rjdmarkdown?color=lightgrey)](https://cran.r-project.org/package=rjdmarkdown)

## Overview

rjdmarkdown gives a set of functions to print nicely your models created by [RJDemetra](https://github.com/nbbrd/rjdemetra).

## Installation

rjdmarkdown relies on RJDemetra that requires Java SE 8 or later version.

```{r gh-installation, eval = FALSE}
# Install development version from GitHub
# install.packages("devtools")
devtools::install_github("AQLT/rjdmarkdown")
```

## Usage

The functions developped are:

- `print_preprocessing()` for the pre-processing model;  
- `print_decomposition()` for the decomposition;  
- `print_diagnostics()` to print diagnostics tests on the quality of the seasonal adjustment.

The available outputs are [LaTeX](https://aqlt.github.io/rjdmarkdown/articles/rjdmarkdown-pdf.pdf) (`format = "latex"`, the package booktabs and float must be used) and [HTML](https://aqlt.github.io/rjdmarkdown/articles/rjdmarkdown-html.html) outputs (`format = "html"`). 

The option `results='asis'` must be used in the chunk:

```{r, eval = FALSE}
library(RJDemetra)
library(rjdmarkdown)
mysa <- x13(ipi_c_eu[, "FR"])
print_preprocessing(mysa, format = "latex")
print_decomposition(mysa, format = "latex")
print_diagnostics(mysa, format = "latex")
```
