---
title: "rjdmarkdown with HTML output"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rjdmarkdown with HTML output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", out.width = "100%",
  fig.dim = c(8, 5), dpi = 300
)
```

The functions developped in `rjdmarkdown` are:

- `print_preprocessing()` for the pre-processing model;  
- `print_decomposition()` for the decomposition.

The result is different between X-13ARIMA and TRAMO-SEATS models.

```{r}
library(rjdmarkdown)
library(RJDemetra)
sa_x13 <- x13(ipi_c_eu[, "FR"])
sa_ts <- tramoseats(ipi_c_eu[, "FR"])
```

# X-13-ARIMA model

```{r, results='asis'}
print_preprocessing(sa_x13, format = "html")
print_decomposition(sa_x13, format = "html", caption = NULL)
```

# TRAMO-SEATS model

```{r, results='asis'}
print_preprocessing(sa_ts, format = "html")
print_decomposition(sa_ts, format = "html", caption = NULL)
```


# Reproductibility
To produce this document, the `knitr` options were set as followed:

```{r, include = TRUE, eval = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", out.width = "100%",
  fig.dim = c(7, 5)
)
```

And the options `results='asis', fig.cap = "S-I Ratio"` were used in the chunks.