---
title: "rjdmarkdown with PDF output"
output: pdf_document
header-includes:
   - \usepackage{booktabs}
   - \usepackage{float}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{here}
vignette: >
  %\VignetteIndexEntry{rjdmarkdown with PDF output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
  comment = "#>", fig.pos = "H"
)
```

The functions developped in `rjdmarkdown` are:

- `print_preprocessing()` for the pre-processing model;  
- `print_decomposition()` for the decomposition.

The result is different between X-13ARIMA and TRAMO-SEATS models.

```{r}
library(rjdmarkdown)
library(RJDemetra)
sa_x13 <- x13(ipi_c_eu[, "FR"])
sa_ts <- tramoseats(ipi_c_eu[, "FR"])
```

# X-13-ARIMA model

```{r, results='asis', fig.cap = "S-I Ratio"}
print_preprocessing(sa_x13, format = "latex")
print_decomposition(sa_x13, format = "latex", caption = NULL)
```

# TRAMO-SEATS model

```{r, results='asis', fig.cap = "S-I Ratio"}
print_preprocessing(sa_ts, format = "latex")
print_decomposition(sa_ts, format = "latex", caption = NULL)
```

# Reproductibility

For PDF outputs, the package `booktabs` and `float` must be used.

```{r, eval = FALSE}
header-includes:
   - \usepackage{booktabs}
   - \usepackage{float}
```

To produce this document, the `knitr` options were set as followed:

```{r, include = TRUE, eval = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
  comment = "#>", fig.pos = "h"
)
```

And the options `results='asis', fig.cap = "S-I Ratio"` were used in the chunks.